A Framework for Classification of Social Machines

### 2013-04-04 latex/old2/sig-alternate.tex
Merge of papers to final version with edits sent to Sheridan

Wikipedia

GalaxyZoo (?)

Ushahidi

Facebook

MechanicalTurk

GWAPs

>>>>

%Wikipedia
%
%GalaxyZoo (?)
%
%Ushahidi
%
%Facebook
%
%MechanicalTurk
%
%GWAPs

In order to demonstrate usage of our framework's constructs, we ranked our social machines
by their Alexa ranking, and performed a full repertory grid elicitation exercise. The
results are illustrated in a grid and accompanying dendrograms for element and construct
similarity in Figure~\ref{dendrogram}.

\begin{figure*}
\begin{center}
\includegraphics[width=18cm]{img/dendrogram.png}
\caption{Dendrogram from a repertory grid exercise of the top 20 (ranked by Alexa) social machines from our element set, against our consolidated constructs.} \label{dendrogram}
\end{center}
\end{figure*}

[needs some discussion on what this shows.]
